CL-PFU: A suite of R packages for energy conversion chain analysis

### 2023-08-10 paper.Rmd
Working on example

```{r}
# Download FAO data for animal muscle work
source(file.path("ExampleFolder", "DownloadScripts", "download_amw_data.R"))
library(targets)
# Run the PFUDatabase pipeline
targets::tar_make(script = file.path("ExampleFolder", "_targets_pfudatabase.R"))

 # Run the PFUAggDatabase pipeline
# targets::tar_make(script = file.path("ExampleFolder", "_targets_pfuaggdatabase.R"))
```

>>>>

```{r}
# (1) Purchase, download, and store IEA data in correct location.
# (2) Download FAO and ILO data for muscle work calculations.
source(file.path("ExampleFolder", "DownloadScripts", "download_amw_data.R"))
# (3) Run the PFUDatabase pipeline
targets::tar_make(script = file.path("ExampleFolder", "_targets_pfudatabase.R"))

# (4) Run the PFUAggDatabase pipeline
# targets::tar_make(script = file.path("ExampleFolder", "_targets_pfuaggdatabase.R"))
```
